---
title: "Interactive Administrative Boundary Maps"
format: 
  html:
    grid:
      body-width: 1100px
    embed-resources: true
toc: true
editor: visual
execute: 
  echo: false
  warning: false
---

These maps are intended to aid understanding of Birmingham's administrative boundaries - specifically, our wards, parliamentary constituencies, districts and localities. Information about deprivation (via IMD 2025 deciles) is also included for reference.

::: callout-note
## Note

All maps on this page are interactive. You can:

-   zoom in and out using the controls in the top left (or use the scroll wheel on your mouse)
-   hover over the map to see more information
-   use the menu in the top right to move between layers, or turn elements on and off
:::

# Birmingham Map

This map allows you to explore Birmingham's wards, parliamentary constituencies, districts and localities.

```{r geojson-data-import}
library(tidyverse)
library(sf)
library(leaflet)
library(DT)
library(readxl)

# import data
# local authority boundary
bham_la24_boundaries <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/Shape files/boundaries-la-districts-2024-wmca.geojson") |> 
  filter(lad24nm == "Birmingham")

# 2024 constituencies
bham_pcon24_boundaries <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/Shape files/birmingham_constituencies_2024_bgc.geojson") |> 
  mutate(pcon24nm = str_replace(pcon24nm, "Birmingham ", ""))

#districts
bham_district22_boundaries <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/Shape files/boundaries-constituencies-2022-wmca.geojson") |> 
  filter(local_authority_name == "Birmingham") |> 
  mutate(pcon22nm = str_replace(pcon22nm, "Birmingham, ", ""))

# create localities from districts
bham_locality_boundaries <- bham_district22_boundaries |> 
  mutate(locality_name = case_when(pcon22nm == "Sutton Coldfield" ~ "North",
                              pcon22nm == "Erdington" ~ "North",
                              pcon22nm == "Perry Barr" ~ "West",
                              pcon22nm == "Ladywood" ~ "West",
                              pcon22nm == "Hodge Hill" ~ "East",
                              pcon22nm == "Yardley" ~ "East",
                              pcon22nm == "Edgbaston" ~ "South",
                              pcon22nm == "Northfield" ~ "South",
                              pcon22nm == "Hall Green" ~ "Central",
                              pcon22nm == "Selly Oak" ~ "Central")) |> 
  group_by(locality_name) |> 
  summarise(do_union = TRUE)

# wards
bham_ward25_boundaries <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/Shape files/boundaries-wards-2025-wmca.geojson") |> 
  filter(lad25nm == "Birmingham")

# GPs
bham_gp_points <- read_csv("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/fingertips-gp-practices_bsol.csv") |> 
  janitor::clean_names() |> 
  filter(grepl("Birmingham", constituency_name) | constituency_name == "Sutton Coldfield")

# make gp dataset a shape file
bham_gp_points <- st_as_sf(bham_gp_points,
                           coords = c("longitude", "latitude"),
                           crs = 4326)

# LSOAs
bham_lsoa21_boundaries <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/Shape files/boundaries-lsoa21-bsol.geojson") |> 
  filter(local_authority_name == "Birmingham")

# IMD 2025 by LSOA
bham_imd25 <- read_csv("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/IMD_2025_England.csv") |> 
  janitor::clean_names() |> 
  filter(local_authority_district_name_2024 == "Birmingham") |> 
  select(lsoa_code_2021, index_of_multiple_deprivation_imd_decile_where_1_is_most_deprived_10_percent_of_lso_as) |> 
  rename(imd25_decile = index_of_multiple_deprivation_imd_decile_where_1_is_most_deprived_10_percent_of_lso_as)

# join LSOA and IMD25 data
bham_imd25 <- bham_lsoa21_boundaries |> 
  left_join(bham_imd25,
            by = join_by("lsoa21cd" == "lsoa_code_2021"))

# import pcn/gp/locality lookup
bham_pcns <- read_excel("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/bsol_gp_pcn_lookup.xlsx",
                         skip = 5) |> 
  janitor::clean_names() |> 
  filter(!is.na(code)) |> 
  rename(locality_name = constituency_locality) |> 
  mutate(post_code = str_replace(post_code, "  ", " "))

# import postcode lookup to get geopoints for PCNs
postcode_lookup <- read_sf("C:/Users/bccaengs/OneDrive - Birmingham City Council/Documents/Work/Useful datasets/postcodes_wmca_dec25.geojson") |> 
  janitor::clean_names() |> 
  select(postcode, local_authority_name, geometry)

# add geopoints to PCNs
bham_pcns <- postcode_lookup |> 
  right_join(bham_pcns,
            by = join_by(postcode == post_code))
```

```{r map-setup}
# set up labels

label_districts <- paste0(bham_district22_boundaries$pcon22nm) |> 
  lapply(htmltools::HTML)

label_pcons24 <- paste0(bham_pcon24_boundaries$pcon24nm) |> 
  lapply(htmltools::HTML)

label_wards25 <- paste0(bham_ward25_boundaries$wd25nm) |> 
  lapply(htmltools::HTML)
label_wards25_wrap <- gsub("\n", "<br>", paste0(str_wrap(bham_ward25_boundaries$wd25nm, 10))) |> 
  lapply(htmltools::HTML)

label_localities <- paste0(bham_locality_boundaries$locality_name) |> 
  lapply(htmltools::HTML)

label_GPs <- paste0(bham_gp_points$surgery_name)|> 
  lapply(htmltools::HTML)

# set colours as variables
highlight_colour <- "red"
border_colour <- "black"
border_sub_colour <- "grey"
ward_text_colour <- "black"
pcon_text_colour <- "black"


viridis_pal <- viridisLite::viridis(10, begin = 0.4, end = 1)

# set up fill palette for imd25
imd25_pal <- colorNumeric(viridis_pal,
                          domain = bham_imd25$imd25_decile,
                          reverse = F)
```

```{r main-map}
# map
leaflet(width = "100%", height = "600px") |> 
  # Define custom panes for strict ordering
  addMapPane("LAPane", zIndex = 200) |>       # LA boundary layer
  addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
  addMapPane("wardsTextPane", zIndex = 350) |> # Wards
  addMapPane("wardsPane", zIndex = 400) |>   
  addMapPane("pconsTextPane", zIndex = 450) |>  # constituencies
  addMapPane("pconsPane", zIndex = 500) |>     
  addMapPane("districtsTextPane", zIndex = 550) |>
  addMapPane("districtsPane", zIndex = 600) |> # Districts
  addMapPane("localitiesTextPane", zIndex = 650) |>
  addMapPane("localitiesPane", zIndex = 700) |># Localities
  addMapPane("markersPane", zIndex = 800) |>   # GP markers
  addMapPane("clustersPane", zIndex = 2000) |>   # GP clusters (top)
  
  # Base tiles
  addTiles(options = tileOptions(opacity = 0.5)) |>
  
  # Birmingham LA boundaries (optional pane if needed)
  addPolygons(data = bham_la24_boundaries,
              color = border_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0.7,
              fillColor = "white",
              options = pathOptions(pane = "LAPane")) |>
  
  # IMD 2025 layer (always bottom)
  addPolygons(data = bham_imd25,
              fillColor = ~imd25_pal(imd25_decile),
              fillOpacity = 0.7,
              color = ~imd25_pal(imd25_decile),
              weight = 1,
              opacity = 0.35,
              stroke = TRUE,
              options = pathOptions(pane = "imdPane"),
              group = "IMD 2025") |>
  
  # Wards
  addPolygons(data = bham_ward25_boundaries,
              color = border_sub_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              label = label_wards25_wrap,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "wardsTextPane"),
              group = "2025 Wards") |>
  
  addPolygons(data = bham_ward25_boundaries,
              color = border_colour,
              weight = 2,
              opacity = 1,
              fillOpacity = 0,
              label = label_wards25,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "wardsPane"),
              group = "2025 Wards") |>
  
  # Constituencies
  addPolygons(data = bham_pcon24_boundaries,
              color = border_sub_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              label = label_pcons24,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "pconsTextPane"),
              group = "2024 Constituencies") |>
  
  addPolygons(data = bham_pcon24_boundaries,
              color = border_colour,
              weight = 2,
              opacity = 1,
              fillOpacity = 0,
              label = label_pcons24,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "pconsPane"),
              group = "2024 Constituencies") |>
  
  # Districts
  addPolygons(data = bham_district22_boundaries,
              color = border_sub_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              label = label_districts,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "districtsTextPane"),
              group = "Districts") |>
  
  addPolygons(data = bham_district22_boundaries,
              color = border_colour,
              weight = 2,
              opacity = 1,
              fillOpacity = 0,
              label = label_districts,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "districtsPane"),
              group = "Districts") |>
  
  # Localities
  addPolygons(data = bham_locality_boundaries,
              color = border_sub_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              label = label_localities,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "localitiesTextPane"),
              group = "Localities") |>
  
  addPolygons(data = bham_locality_boundaries,
              color = border_colour,
              weight = 2,
              opacity = 1,
              fillOpacity = 0,
              label = label_localities,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "localitiesPane"),
              group = "Localities") |>
  
  # # GP markers (top)
  # addMarkers(data = bham_gp_points,
  #            label = label_GPs,
  #            group = "GP Surgeries",
  #            clusterOptions = markerClusterOptions(
  #              pane = "clustersPane",  # Keep clusters above labels
  #              iconCreateFunction = JS("
  #   function (cluster) {
  #     var count = cluster.getChildCount();
  #     
  #     // Dynamic size based on count
  #     var size = count < 10 ? 40 : (count < 20 ? 50 : 60);
  #     var innerSize = size * 0.7; // Inner circle smaller
  #     
  #     var color = '#D00070'; // Fixed color for all clusters
  #     
  #     return new L.DivIcon({
  #       html: '<div style=\"position:relative; width:' + size + 'px; height:' + size + 'px;\">' +
  #               '<div style=\"background-color:' + color + '; opacity:0.4; border-radius:50%; width:' + size + 'px; height:' + size + 'px; position:absolute; top:0; left:0;\"></div>' +
  #               '<div style=\"background-color:' + color + '; color:white; border-radius:50%; width:' + innerSize + 'px; height:' + innerSize + 'px; position:absolute; top:' + ((size - innerSize)/2) + 'px; left:' + ((size - innerSize)/2) + 'px; display:flex; align-items:center; justify-content:center; font-weight:bold;\">' + count + '</div>' +
  #             '</div>',
  #       className: 'marker-cluster',
  #       iconSize: [size, size],
  #       pane: 'clustersPane'
  #     });
  #   }
  # ")
  #            ),
  #            options = markerOptions(pane = "markersPane")) |>
  
  # Legend
  addLegend(data = bham_imd25,
            "bottomright", 
            pal = imd25_pal, 
            values = ~imd25_decile,
            title = "IMD 2025 Decile",
            labFormat = labelFormat(prefix = "Decile "),
            opacity = 0.7) |>
  
  # Layer control
  addLayersControl(
    baseGroups = c("2025 Wards", "2024 Constituencies", "Districts", "Localities"),
    overlayGroups = c("IMD 2025"),
    options = layersControlOptions(collapsed = FALSE)
  )
```

# District-Ward Maps

These maps visualise the interaction between wards and districts in Birmingham. Some wards fit neatly inside a district boundary; others do not. Hovering over a ward will show you what proportion of that ward fits inside the district boundary.

Use the tabs to move between districts. A table is provided in the final tab as a quick lookup between districts and wards - this can be filtered or sorted as needed.

```{r district-map-setup}
district_wards_full <- data.frame()
district_wards <- data.frame()

districts <- bham_district22_boundaries$pcon22nm

for (district in districts) {
  # clip wards inside district boundary
  temp_district_wards <- bham_district22_boundaries |> 
    filter(pcon22nm == district)|> 
    st_intersection(bham_ward25_boundaries) |> 
    mutate(district_name = district)
  
  # find out the area of each clipped ward
  temp_district_wards$area <- st_area(temp_district_wards)
  
  # pull out unclipped wards for this district
  temp_district_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_district_wards$wd25cd) |> 
    mutate(district_name = district)
  
  # find area of unclipped ward and add to clipped ward sf
  temp_district_wards$full_area <- st_area(temp_district_wards_full)
  
  # calulate what % of each ward is inside the boundary
  # then filter out wards with less than 1% area inside boundary
  temp_district_wards <- temp_district_wards |> 
    mutate(pct = area/full_area*100) |> 
    filter(as.numeric(pct) > 1)
  
  # recalculate unclipped wards now wards with <1% are excluded
 temp_district_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_district_wards$wd25cd) |> 
   mutate(district_name = district)
 
 # append temp dfs to main df
 district_wards_full <- rbind(district_wards_full,
                             temp_district_wards_full)

 district_wards <- rbind(district_wards,
                         temp_district_wards)
}

# district lsoa maps
district_lsoas <- data.frame()

for (district in districts) {
  # clip wards inside district boundary
  temp_district_lsoas <- bham_district22_boundaries |> 
    filter(pcon22nm == district)|> 
    st_intersection(bham_imd25) |> 
    mutate(district_name = district)

  district_lsoas <- rbind(district_lsoas,
                          temp_district_lsoas)
}

# filter to get gps which fall within each district boundary
district_gp_points <- data.frame()

for (district in districts) {
  temp_district_gp_list <- bham_district22_boundaries |> 
    filter(pcon22nm == district) |> 
    st_contains(bham_gp_points)
  
  temp_district_gp_list <- temp_district_gp_list[[1]]
  
  temp_district_gp_points <- bham_gp_points |> 
    filter(row_number() %in% temp_district_gp_list) |> 
    mutate(district_name = district)
  
  district_gp_points <- rbind(district_gp_points,
                              temp_district_gp_points)
}

# function to create map
make_district_ward_map <- function(district, zoom) {
  # wrapped ward names for district map
  label_wards25_wrap_district <- district_wards |> 
    filter(district_name == district) |> 
    pull(wd25nm) |> 
    str_wrap(15)
  label_wards25_wrap_district<- gsub("\n", "<br>", label_wards25_wrap_district) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside district for district map
  label_wards25_district <- district_wards |> 
    filter(district_name == district) |> 
    mutate(label = paste0(wd25nm, "<br>",
                          round(pct, 0), "% falls within ", district_name)) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  lat <- bham_district22_boundaries |> 
    filter(pcon22nm == district) |> 
    pull(lat)
  
  long <- bham_district22_boundaries |> 
    filter(pcon22nm == district) |> 
    pull(long)
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("districtPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("wardsTextPane", zIndex = 350) |>
    addMapPane("wardsPane", zIndex = 400) |>     # Wards
    addMapPane("markersPane", zIndex = 700) |>   # GP markers
    addMapPane("clustersPane", zIndex = 2000) |>   # GP clusters (top)
    #addMapPane("clustersPane", zIndex = 2000) |>
    addTiles(options = tileOptions(opacity = 0.5)) |> 
    # display district of interest only
    addPolygons(data = bham_district22_boundaries |> filter(pcon22nm == district),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.7,
                fillColor = "white",
                options = pathOptions(pane = "districtPane")) |>
    # display IMD by LSOA for district of interest only
    addPolygons(data = district_lsoas |> filter(district_name == district),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.35,
                stroke = T,
                group = "IMD 2025",
                options = pathOptions(pane = "imdPane")) |>
    # full wards text only
    addPolygons(data = district_wards_full |> filter(district_name == district),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_wards25_wrap_district,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "wardsTextPane"),
                group = "Full Wards") |>
    # full wards
    addPolygons(data = district_wards_full |> filter(district_name == district),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                #label = ~wd25nm,
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_wards25_district,
                options = pathOptions(pane = "wardsPane"),
                group = "Full Wards") |>
  #   addMarkers(data = district_gp_points |> filter(district_name == district),
  #              label = ~surgery_name,
  #              group = "GP Surgeries",
  #              options = pathOptions(pane = "markersPane"),
  #              clusterOptions = markerClusterOptions(
  #                pane = "clustersPane",  # Keep clusters above labels
  #                iconCreateFunction = JS("
  #   function (cluster) {
  #     var count = cluster.getChildCount();
  #     
  #     // Dynamic size based on count
  #     var size = count < 10 ? 40 : (count < 20 ? 50 : 60);
  #     var innerSize = size * 0.7; // Inner circle smaller
  #     
  #     var color = '#D00070'; // Fixed color for all clusters
  #     
  #     return new L.DivIcon({
  #       html: '<div style=\"position:relative; width:' + size + 'px; height:' + size + 'px;\">' +
  #               '<div style=\"background-color:' + color + '; opacity:0.4; border-radius:50%; width:' + size + 'px; height:' + size + 'px; position:absolute; top:0; left:0;\"></div>' +
  #               '<div style=\"background-color:' + color + '; color:white; border-radius:50%; width:' + innerSize + 'px; height:' + innerSize + 'px; position:absolute; top:' + ((size - innerSize)/2) + 'px; left:' + ((size - innerSize)/2) + 'px; display:flex; align-items:center; justify-content:center; font-weight:bold;\">' + count + '</div>' +
  #             '</div>',
  #       className: 'marker-cluster',
  #       iconSize: [size, size],
  #       pane: 'clustersPane'
  #     });
  #   }
  # ")
  #              ),) |>
    addLegend(data = district_lsoas,
              "bottomright", 
              pal = imd25_pal, 
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |> 
    setView(lat = lat, lng = long, zoom = zoom) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025"))
  
}
```

::: panel-tabset
## Edgbaston

```{r edgbaston-ward-map}
make_district_ward_map("Edgbaston", 13)
```

## Erdington

```{r erdington-ward-map}
make_district_ward_map("Erdington", 13)
```

## Hall Green

```{r hall-green-ward-map}
make_district_ward_map("Hall Green", 13)
```

## Hodge Hill

```{r hodge-hill-ward-map}
make_district_ward_map("Hodge Hill", 13)
```

## Ladywood

```{r ladywood-ward-map}
make_district_ward_map("Ladywood", 13)
```

## Northfield

```{r Northfield-ward-map}
make_district_ward_map("Northfield", 13)
```

## Perry Barr

```{r perry-barr-ward-map}
make_district_ward_map("Perry Barr", 13)
```

## Selly Oak

```{r selly-oak-ward-map}
make_district_ward_map("Selly Oak", 13)
```

## Sutton Coldfield

```{r sutton-ward-map}
make_district_ward_map("Sutton Coldfield", 12)
```

## Yardley

```{r Yardley-ward-map}
make_district_ward_map("Yardley", 13)
```

## Table

```{r district-ward-table}
district_wards |> 
  as_tibble() |> 
  select(wd25nm, pcon22nm, pct) |> 
  arrange(wd25nm) |> 
  mutate(pct = round(pct, 0),
         pct = paste0(pct, "%")) |> 
  rename(`Ward name` = wd25nm,
         `District name` = pcon22nm,
         `% of ward in district` = pct) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))
```
:::

# Constituency-Ward Maps

These maps visualise the interaction between wards and parliamentary constituencies in Birmingham. Some wards fit neatly inside a constituency boundary; others do not. Hovering over a ward will show you what proportion of that ward fits inside the constituency boundary.

Use the tabs to move between constituencies. A table is provided in the final tab as a quick lookup between constituencies and wards - this can be filtered or sorted as needed.

```{r pcon-map-setup}
pcon_wards_full <- data.frame()
pcon_wards <- data.frame()

pcons <- bham_pcon24_boundaries$pcon24nm

for (pcon in pcons) {
  # clip wards inside pcon boundary
  temp_pcon_wards <- bham_pcon24_boundaries |> 
    filter(pcon24nm == pcon)|> 
    st_intersection(bham_ward25_boundaries) |> 
    mutate(pcon_name = pcon)
  
  # find out the area of each clipped ward
  temp_pcon_wards$area <- st_area(temp_pcon_wards)
  
  # pull out unclipped wards for this pcon
  temp_pcon_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_pcon_wards$wd25cd) |> 
    mutate(pcon_name = pcon)
  
  # find area of unclipped ward and add to clipped ward sf
  temp_pcon_wards$full_area <- st_area(temp_pcon_wards_full)
  
  # calulate what % of each ward is inside the boundary
  # then filter out wards with less than 1% area inside boundary
  temp_pcon_wards <- temp_pcon_wards |> 
    mutate(pct = area/full_area*100) |> 
    filter(as.numeric(pct) > 1)
  
  # recalculate unclipped wards now wards with <1% are excluded
  temp_pcon_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_pcon_wards$wd25cd) |> 
    mutate(pcon_name = pcon)
  
  # append temp dfs to main df
  pcon_wards_full <- rbind(pcon_wards_full,
                               temp_pcon_wards_full)
  
  pcon_wards <- rbind(pcon_wards,
                          temp_pcon_wards)
}

# pcon lsoa maps
pcon_lsoas <- data.frame()

for (pcon in pcons) {
  # clip wards inside pcon boundary
  temp_pcon_lsoas <- bham_pcon24_boundaries |> 
    filter(pcon24nm == pcon)|> 
    st_intersection(bham_imd25) |> 
    mutate(pcon_name = pcon)
  
  pcon_lsoas <- rbind(pcon_lsoas,
                          temp_pcon_lsoas)
}

# filter to get gps which fall within each pcon boundary
pcon_gp_points <- data.frame()

for (pcon in pcons) {
  temp_pcon_gp_list <- bham_pcon24_boundaries |> 
    filter(pcon24nm == pcon) |> 
    st_contains(bham_gp_points)
  
  temp_pcon_gp_list <- temp_pcon_gp_list[[1]]
  
  temp_pcon_gp_points <- bham_gp_points |> 
    filter(row_number() %in% temp_pcon_gp_list) |> 
    mutate(pcon_name = pcon)
  
  pcon_gp_points <- rbind(pcon_gp_points,
                              temp_pcon_gp_points)
}

# function to create map
make_pcon_ward_map <- function(pcon, zoom) {
  # wrapped ward names for district map
  label_wards25_wrap_pcon <- pcon_wards |> 
    filter(pcon_name == pcon) |> 
    pull(wd25nm) |> 
    str_wrap(15)
  label_wards25_wrap_pcon<- gsub("\n", "<br>", label_wards25_wrap_pcon) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside pcon for pcon map
  label_wards25_pcon <- pcon_wards |> 
    filter(pcon_name == pcon) |> 
    mutate(label = paste0(wd25nm, "<br>",
                          round(pct, 0), "% falls within ", pcon_name)) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  lat <- bham_pcon24_boundaries |> 
    filter(pcon24nm == pcon) |> 
    pull(lat)
  
  long <- bham_pcon24_boundaries |> 
    filter(pcon24nm == pcon) |> 
    pull(long)
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("pconPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("wardsTextPane", zIndex = 350) |>
    addMapPane("wardsPane", zIndex = 400) |>     # Wards
    addMapPane("markersPane", zIndex = 700) |>   # GP markers
    addMapPane("clustersPane", zIndex = 2000) |>   # GP clusters (top)
    addTiles(options = tileOptions(opacity = 0.5)) |> 
    # display pcon of interest only
    addPolygons(data = bham_pcon24_boundaries |> filter(pcon24nm == pcon),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.7,
                fillColor = "white",
                options = pathOptions(pane = "pconPane")) |>
    # display IMD by LSOA for pcon of interest only
    addPolygons(data = pcon_lsoas |> filter(pcon_name == pcon),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.35,
                stroke = T,
                group = "IMD 2025",
                options = pathOptions(pane = "imdPane")) |>
    # full wards text only
    addPolygons(data = pcon_wards_full |> filter(pcon_name == pcon),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_wards25_wrap_pcon,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "wardsTextPane"),
                group = "Full Wards") |>
    # full wards
    addPolygons(data = pcon_wards_full |> filter(pcon_name == pcon),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                #label = ~wd25nm,
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_wards25_pcon,
                options = pathOptions(pane = "wardsPane"),
                group = "Full Wards") |>
  #   addMarkers(data = pcon_gp_points |> filter(pcon_name == pcon),
  #              label = ~surgery_name,
  #              group = "GP Surgeries",
  #              options = pathOptions(pane = "markersPane"),
  #              clusterOptions = markerClusterOptions(
  #                pane = "clustersPane",  # Keep clusters above labels
  #                iconCreateFunction = JS("
  #   function (cluster) {
  #     var count = cluster.getChildCount();
  #     
  #     // Dynamic size based on count
  #     var size = count < 10 ? 40 : (count < 20 ? 50 : 60);
  #     var innerSize = size * 0.7; // Inner circle smaller
  #     
  #     var color = '#D00070'; // Fixed color for all clusters
  #     
  #     return new L.DivIcon({
  #       html: '<div style=\"position:relative; width:' + size + 'px; height:' + size + 'px;\">' +
  #               '<div style=\"background-color:' + color + '; opacity:0.4; border-radius:50%; width:' + size + 'px; height:' + size + 'px; position:absolute; top:0; left:0;\"></div>' +
  #               '<div style=\"background-color:' + color + '; color:white; border-radius:50%; width:' + innerSize + 'px; height:' + innerSize + 'px; position:absolute; top:' + ((size - innerSize)/2) + 'px; left:' + ((size - innerSize)/2) + 'px; display:flex; align-items:center; justify-content:center; font-weight:bold;\">' + count + '</div>' +
  #             '</div>',
  #       className: 'marker-cluster',
  #       iconSize: [size, size],
  #       pane: 'clustersPane'
  #     });
  #   }
  # ")
  #              )) |>
    addLegend(data = pcon_lsoas,
              "bottomright", 
              pal = imd25_pal, 
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |> 
    setView(lat = lat, lng = long, zoom = zoom) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025"))
  
}
```

::: panel-tabset
## Edgbaston

```{r edgbaston-pcon-ward-map}
make_pcon_ward_map("Edgbaston", 13)
```

## Erdington

```{r erdington-pcon-ward-map}
make_pcon_ward_map("Erdington", 13)
```

## Hall Green & Moseley

```{r hall-green-pcon-ward-map}
make_pcon_ward_map("Hall Green and Moseley", 13)
```

## Hodge Hill & Solihull North

```{r hodge-hill-pcon-ward-map}
make_pcon_ward_map("Hodge Hill and Solihull North", 13)
```

## Ladywood

```{r ladywood-pcon-ward-map}
make_pcon_ward_map("Ladywood", 13)
```

## Northfield

```{r Northfield-pcon-ward-map}
make_pcon_ward_map("Northfield", 13)
```

## Perry Barr

```{r perry-barr-pcon-ward-map}
make_pcon_ward_map("Perry Barr", 13)
```

## Selly Oak

```{r selly-oak-pcon-ward-map}
make_pcon_ward_map("Selly Oak", 13)
```

## Sutton Coldfield

```{r sutton-pcon-ward-map}
make_pcon_ward_map("Sutton Coldfield", 12)
```

## Yardley

```{r Yardley-pcon-ward-map}
make_pcon_ward_map("Yardley", 13)
```

## Table

```{r pcon-ward-table}
pcon_wards |> 
  as_tibble() |> 
  select(wd25nm, pcon_name, pct) |> 
  arrange(wd25nm) |> 
  mutate(pct = round(pct, 0),
         pct = paste0(pct, "%")) |> 
  rename(`Ward name` = wd25nm,
         `Constituency name` = pcon_name,
         `% of ward in constituency` = pct) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))
```
:::

# Locality-Ward Maps

These maps visualise the interaction between wards and localities in Birmingham. Some wards fit neatly inside a locality boundary; others do not. Hovering over a ward will show you what proportion of that ward fits inside the locality boundary.

Use the tabs to move between localities. A table is provided in the final tab as a quick lookup between localities and wards - this can be filtered or sorted as needed.

```{r locality-map-setup}
locality_wards_full <- data.frame()
locality_wards <- data.frame()

sf_use_s2(FALSE)

localities <- bham_locality_boundaries$locality_name

for (locality in localities) {
  # clip wards inside district boundary
  temp_locality_wards <- bham_locality_boundaries |> 
    filter(locality_name == locality)|> 
    st_intersection(bham_ward25_boundaries) |> 
    mutate(locality_name = locality)
  
  # find out the area of each clipped ward
  temp_locality_wards$area <- st_area(temp_locality_wards)
  
  # pull out unclipped wards for this locality
  temp_locality_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_locality_wards$wd25cd) |> 
    mutate(locality_name = locality)
  
  # find area of unclipped ward and add to clipped ward sf
  temp_locality_wards$full_area <- st_area(temp_locality_wards_full)
  
  # calulate what % of each ward is inside the boundary
  # then filter out wards with less than 1% area inside boundary
  temp_locality_wards <- temp_locality_wards |> 
    mutate(pct = area/full_area*100) |> 
    filter(as.numeric(pct) > 1)
  
  # recalculate unclipped wards now wards with <1% are excluded
 temp_locality_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_locality_wards$wd25cd) |> 
   mutate(locality_name = locality)
 
 # append temp dfs to main df
 locality_wards_full <- rbind(locality_wards_full,
                             temp_locality_wards_full)

 locality_wards <- rbind(locality_wards,
                         temp_locality_wards)
}

# locality lsoa maps
locality_lsoas <- data.frame()

for (locality in localities) {
  # clip wards inside locality boundary
  temp_locality_lsoas <- bham_locality_boundaries |> 
    filter(locality_name == locality)|> 
    st_intersection(bham_imd25) |> 
    mutate(locality_name = locality)

  locality_lsoas <- rbind(locality_lsoas,
                          temp_locality_lsoas)
}

# filter to get gps which fall within each locality boundary
locality_gp_points <- data.frame()

for (locality in localities) {
  temp_locality_gp_list <- bham_locality_boundaries |> 
    filter(locality_name == locality) |> 
    st_contains(bham_gp_points)
  
  temp_locality_gp_list <- temp_locality_gp_list[[1]]
  
  temp_locality_gp_points <- bham_gp_points |> 
    filter(row_number() %in% temp_locality_gp_list) |> 
    mutate(locality_name = locality)
  
  locality_gp_points <- rbind(locality_gp_points,
                              temp_locality_gp_points)
}

# function for making locality maps
make_locality_ward_map <- function(locality) {
  # wrapped ward names for district map
  label_wards25_wrap_locality <- locality_wards |> 
    filter(locality_name == locality) |> 
    pull(wd25nm) |> 
    str_wrap(15)
  label_wards25_wrap_locality<- gsub("\n", "<br>", label_wards25_wrap_locality) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside locality for locality map
  label_wards25_locality <- locality_wards |> 
    filter(locality_name == locality) |> 
    mutate(label = paste0(wd25nm, "<br>",
                          round(pct, 0), "% falls within ", locality_name, " locality")) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  # gp labels for locality map
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("localityPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("wardsTextPane", zIndex = 350) |>
    addMapPane("wardsPane", zIndex = 400) |>     # Wards
    addMapPane("markersPane", zIndex = 700) |>   # GP markers
    addMapPane("clustersPane", zIndex = 2000) |>   # GP clusters (top)
    addTiles(options = tileOptions(opacity = 0.5)) |> 
    # display locality of interest only
    addPolygons(data = bham_locality_boundaries |> filter(locality_name == locality),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.6,
                fillColor = "white",
                options = pathOptions(pane = "localityPane")) |>
    # display IMD by LSOA for district of interest only
    addPolygons(data = locality_lsoas |> filter(locality_name == locality),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.2,
                stroke = F,
                options = pathOptions(pane = "imdPane"),
                group = "IMD 2025") |>
    # full wards text only
    addPolygons(data = locality_wards_full |> filter(locality_name == locality),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_wards25_wrap_locality,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "wardsTextPane"),
                group = "Full Wards") |>
    # full wards
    addPolygons(data = locality_wards_full |> filter(locality_name == locality),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_wards25_locality,
                options = pathOptions(pane = "wardsPane"),
                group = "Full Wards") |>
  #   addMarkers(data = locality_gp_points |> filter(locality_name == locality),
  #              label = ~surgery_name,
  #              group = "GP Surgeries",
  #              options = pathOptions(pane = "markersPane"),
  #              clusterOptions = markerClusterOptions(
  #                pane = "clustersPane",  # Keep clusters above labels
  #                iconCreateFunction = JS("
  #   function (cluster) {
  #     var count = cluster.getChildCount();
  #     
  #     // Dynamic size based on count
  #     var size = count < 10 ? 40 : (count < 20 ? 50 : 60);
  #     var innerSize = size * 0.7; // Inner circle smaller
  #     
  #     var color = '#D00070'; // Fixed color for all clusters
  #     
  #     return new L.DivIcon({
  #       html: '<div style=\"position:relative; width:' + size + 'px; height:' + size + 'px;\">' +
  #               '<div style=\"background-color:' + color + '; opacity:0.4; border-radius:50%; width:' + size + 'px; height:' + size + 'px; position:absolute; top:0; left:0;\"></div>' +
  #               '<div style=\"background-color:' + color + '; color:white; border-radius:50%; width:' + innerSize + 'px; height:' + innerSize + 'px; position:absolute; top:' + ((size - innerSize)/2) + 'px; left:' + ((size - innerSize)/2) + 'px; display:flex; align-items:center; justify-content:center; font-weight:bold;\">' + count + '</div>' +
  #             '</div>',
  #       className: 'marker-cluster',
  #       iconSize: [size, size],
  #       pane: 'clustersPane'
  #     });
  #   }
  # ")
  #              )) |>
    addLegend(data = locality_lsoas,
              "bottomright", 
              pal = imd25_pal, 
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |> 
    #setView(lat = 52.4491, lng = -1.96463, zoom = 13) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025"))
}
```

::: panel-tabset
## North

```{r north-ward-map}
make_locality_ward_map("North")
```

## East

```{r East-ward-map}
make_locality_ward_map("East")
```

## South

```{r South-ward-map}
make_locality_ward_map("South")
```

## West

```{r West-ward-map}
make_locality_ward_map("West")
```

## Central

```{r Central-ward-map}
make_locality_ward_map("Central")
```

## Table

```{r locality-ward-table}
locality_wards |> 
  as_tibble() |> 
  select(wd25nm, locality_name, pct) |> 
  arrange(wd25nm) |> 
  mutate(pct = round(pct, 0),
         pct = paste0(pct, "%")) |> 
  rename(`Ward name` = wd25nm,
         `Locality name` = locality_name,
         `% of ward in locality` = pct) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))
```
:::

# Locality-Constituency Maps

These maps visualise the interaction between 2024 parliamentary constituencies and localities in Birmingham. Some constituencies fit neatly inside a locality boundary; others do not. Hovering over a constituency will show you what proportion of that constituency fits inside the locality boundary.

Use the tabs to move between localities. A table is provided in the final tab as a quick lookup between localities and constituencies - this can be filtered or sorted as needed.

```{r locality-pcon-map-setup}
locality_pcons_full <- data.frame()
locality_pcons <- data.frame()

sf_use_s2(FALSE)

localities <- bham_locality_boundaries$locality_name

for (locality in localities) {
  # clip pcons inside district boundary
  temp_locality_pcons <- bham_locality_boundaries |> 
    filter(locality_name == locality)|> 
    st_intersection(bham_pcon24_boundaries) |> 
    mutate(locality_name = locality)
  
  # find out the area of each clipped pcon
  temp_locality_pcons$area <- st_area(temp_locality_pcons)
  
  # pull out unclipped pcons for this locality
  temp_locality_pcons_full <- bham_pcon24_boundaries |> 
    filter(pcon24nm %in% temp_locality_pcons$pcon24nm) |> 
    mutate(locality_name = locality)
  
  # find area of unclipped pcon and add to clipped pcon sf
  temp_locality_pcons$full_area <- st_area(temp_locality_pcons_full)
  
  # calulate what % of each pcon is inside the boundary
  # then filter out pcons with less than 1% area inside boundary
  temp_locality_pcons <- temp_locality_pcons |> 
    mutate(pct = area/full_area*100) |> 
    filter(as.numeric(pct) > 1)
  
  # recalculate unclipped pcons now pcons with <1% are excluded
  temp_locality_pcons_full <- bham_pcon24_boundaries |> 
    filter(pcon24nm %in% temp_locality_pcons$pcon24nm) |> 
    mutate(locality_name = locality)
  
  # append temp dfs to main df
  locality_pcons_full <- rbind(locality_pcons_full,
                               temp_locality_pcons_full)
  
  locality_pcons <- rbind(locality_pcons,
                          temp_locality_pcons)
}

# function for making locality maps
make_locality_pcon_map <- function(locality) {
  # wrapped pcon names for district map
  label_pcons24_wrap_locality <- locality_pcons |> 
    filter(locality_name == locality) |> 
    pull(pcon24nm) |> 
    str_wrap(15)
  label_pcons24_wrap_locality<- gsub("\n", "<br>", label_pcons24_wrap_locality) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside locality for locality map
  label_pcons24_locality <- locality_pcons |> 
    filter(locality_name == locality) |> 
    mutate(label = paste0(pcon24nm, " constituency", "<br>",
                          round(pct, 0), "% falls within ", locality_name, " locality")) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  # gp labels for locality map
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("localityPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("pconsTextPane", zIndex = 350) |>
    addMapPane("pconsPane", zIndex = 400) |>     # pcons
    addMapPane("markersPane", zIndex = 700) |>   # GP markers
    addMapPane("clustersPane", zIndex = 2000) |>   # GP clusters (top)
    addTiles(options = tileOptions(opacity = 0.5)) |> 
    # display locality of interest only
    addPolygons(data = bham_locality_boundaries |> filter(locality_name == locality),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.6,
                fillColor = "white",
                options = pathOptions(pane = "localityPane")) |>
    # display IMD by LSOA for district of interest only
    addPolygons(data = locality_lsoas |> filter(locality_name == locality),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.2,
                stroke = F,
                options = pathOptions(pane = "imdPane"),
                group = "IMD 2025") |>
    # full pcons text only
    addPolygons(data = locality_pcons_full |> filter(locality_name == locality),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_pcons24_wrap_locality,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = pcon_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "pconsTextPane"),
                group = "Full pcons") |>
    # full pcons
    addPolygons(data = locality_pcons_full |> filter(locality_name == locality),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_pcons24_locality,
                options = pathOptions(pane = "pconsPane"),
                group = "Full pcons") |>
  #   addMarkers(data = locality_gp_points |> filter(locality_name == locality),
  #              label = ~surgery_name,
  #              group = "GP Surgeries",
  #              options = pathOptions(pane = "markersPane"),
  #              clusterOptions = markerClusterOptions(
  #                pane = "clustersPane",  # Keep clusters above labels
  #                iconCreateFunction = JS("
  #   function (cluster) {
  #     var count = cluster.getChildCount();
  #     
  #     // Dynamic size based on count
  #     var size = count < 10 ? 40 : (count < 20 ? 50 : 60);
  #     var innerSize = size * 0.7; // Inner circle smaller
  #     
  #     var color = '#D00070'; // Fixed color for all clusters
  #     
  #     return new L.DivIcon({
  #       html: '<div style=\"position:relative; width:' + size + 'px; height:' + size + 'px;\">' +
  #               '<div style=\"background-color:' + color + '; opacity:0.4; border-radius:50%; width:' + size + 'px; height:' + size + 'px; position:absolute; top:0; left:0;\"></div>' +
  #               '<div style=\"background-color:' + color + '; color:white; border-radius:50%; width:' + innerSize + 'px; height:' + innerSize + 'px; position:absolute; top:' + ((size - innerSize)/2) + 'px; left:' + ((size - innerSize)/2) + 'px; display:flex; align-items:center; justify-content:center; font-weight:bold;\">' + count + '</div>' +
  #             '</div>',
  #       className: 'marker-cluster',
  #       iconSize: [size, size],
  #       pane: 'clustersPane'
  #     });
  #   }
  # ")
  #              )) |>
    addLegend(data = locality_lsoas,
              "bottomright", 
              pal = imd25_pal, 
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |> 
    #setView(lat = 52.4491, lng = -1.96463, zoom = 13) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025"))
}
```

::: panel-tabset
## North

```{r north-pcon-map}
make_locality_pcon_map("North")
```

## East

```{r East-pcon-map}
make_locality_pcon_map("East")
```

## South

```{r South-pcon-map}
make_locality_pcon_map("South")
```

## West

```{r West-pcon-map}
make_locality_pcon_map("West")
```

## Central

```{r Central-pcon-map}
make_locality_pcon_map("Central")
```

## Table

```{r locality-pcon-table}
locality_pcons |> 
  as_tibble() |> 
  select(pcon24nm, locality_name, pct) |> 
  arrange(pcon24nm) |> 
  mutate(pct = round(pct, 0),
         pct = paste0(pct, "%")) |> 
  rename(`Constituency name` = pcon24nm,
         `Locality name` = locality_name,
         `% of constituency in locality` = pct) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))
```
:::

# Locality-PCN Maps

These maps visualise the interaction between primary care networks (PCNs) and their assigned localities in Birmingham. Individual GP practices are shown and coloured according to their PCN. Some practices fall inside their PCN's assigned locality; others do not. Hovering over a point will show you the GP practice name, PCN and type (main/branch).

Use the tabs to move between localities. The table in the final tab provides a summary of how many practices fall outside of their assigned locality, by locality and PCN - this can be filtered or sorted as needed.

```{r locality-pcn-map-setup}
make_locality_pcn_map <- function(locality){
  locality_data <- bham_pcns |>
    filter(locality_name == locality)
  
  label_pcn_GPs <- paste0(locality_data$prac_name, "<br>",
                          locality_data$pcn, "<br>",
                          locality_data$type)|> 
    lapply(htmltools::HTML)
  
  pal <- colorFactor(
    palette = "Dark2",   # or another palette name
    domain = locality_data$pcn
  )
  
  leaflet(locality_data,
          width = "100%", height = "650px") |> 
    addTiles(options = tileOptions(opacity = 0.5)) |>
    addPolygons(data = bham_locality_boundaries |> filter(locality_name == locality),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.6,
                fillColor = "white") |>
    addCircleMarkers(color = ~pal(pcn),
                     fillColor = ~pal(pcn),
                     fillOpacity = 1,
                     radius = 8,
                     stroke = FALSE,
                     label = label_pcn_GPs) |> 
    addLegend(
      "bottomright",
      pal = pal,
      values = ~pcn,
      title = "PCN"
    )
}
```

::: panel-tabset
## North

```{r north-pcn-map}
make_locality_pcn_map("North")
```

## East

```{r East-pcn-map}
make_locality_pcn_map("East")
```

## South

```{r South-pcn-map}
make_locality_pcn_map("South")
```

## West

```{r West-pcn-map}
make_locality_pcn_map("West")
```

## Central

```{r Central-pcn-map}
make_locality_pcn_map("Central")
```

## Table

```{r locality-pcn-table}
locality_pcn_table <- data.frame()

for (locality in localities){
  temp_locality_pcns <- bham_pcns |>
    filter(locality_name == locality)
  
  temp_locality_pcn_matrix <- bham_locality_boundaries |>
    filter(locality_name == locality) |> 
    st_contains(temp_locality_pcns,
                sparse = F)
  
  row.names(temp_locality_pcn_matrix) <- locality
  
  colnames(temp_locality_pcn_matrix) <- temp_locality_pcns$prac_name
  
  temp_locality_pcn_matrix <- temp_locality_pcn_matrix |> 
    as_tibble(rownames = "locality_name") |> 
    pivot_longer(cols = !locality_name,
                 names_to = "prac_name",
                 values_to = "in_locality")
  
  locality_pcn_table <- rbind(locality_pcn_table,
                              temp_locality_pcn_matrix)
}

# locality_pcn_table |> 
#   left_join(bham_pcns,
#             by = c("locality_name", "prac_name")) |> 
#   select(locality_name, pcn, prac_name, in_locality) |> 
#   rename(`Locality` = locality_name,
#          PCN = pcn,
#          `Practice Name` = prac_name,
#          `Falls inside assigned locality` = in_locality) |> 
#   datatable(rownames = F,
#             filter = "top",
#             options = list(pageLength = 15,
#                            autoWidth = TRUE))


locality_pcn_table |> 
  left_join(bham_pcns,
            by = c("locality_name", "prac_name")) |> 
  select(locality_name, pcn, prac_name, in_locality) |> 
  group_by(locality_name, pcn, in_locality) |> 
  count() |> 
  #ungroup() |> 
  group_by(locality_name, pcn) |> 
  mutate(d = sum(n)) |> 
  filter(in_locality == F) |> 
  mutate(pct = n/d*100,
         label = paste0(round(pct, 1), "% (", n, " out of ", d, " practices)")) |> 
  select(locality_name, pcn, label) |> 
  rename(`Locality` = locality_name,
         PCN = pcn,
         `Practices falling outside assigned locality` = label) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))

```
:::
