---
title: "Interactive Administrative Boundary Maps"
format: 
  html:
    grid:
      body-width: 1100px
    embed-resources: true
toc: true
editor: visual
execute: 
  echo: false
  warning: false
---

```{r geojson-data-import}
library(tidyverse)
library(sf)
library(leaflet)
library(DT)
library(readxl)

# set tile opacity as variable
tile_opacity <- 0

# set file paths from .Renviron file
shape_file_path <- Sys.getenv("shape_file_path")
data_file_path <- Sys.getenv("data_file_path")

# import data
# local authority boundary
bham_la24_boundaries <- read_sf(paste0(shape_file_path, "boundaries-la-districts-2024-wmca.geojson")) |> 
  filter(lad24nm == "Birmingham")

#districts
bham_district22_boundaries <- read_sf(paste0(shape_file_path, "boundaries-constituencies-2022-wmca.geojson")) |> 
  filter(local_authority_name == "Birmingham") |> 
  mutate(pcon22nm = str_replace(pcon22nm, "Birmingham, ", ""))

# create localities from districts
bham_locality_boundaries <- bham_district22_boundaries |> 
  mutate(locality = case_when(pcon22nm == "Sutton Coldfield" ~ "North",
                              pcon22nm == "Erdington" ~ "North",
                              pcon22nm == "Perry Barr" ~ "West",
                              pcon22nm == "Ladywood" ~ "West",
                              pcon22nm == "Hodge Hill" ~ "East",
                              pcon22nm == "Yardley" ~ "East",
                              pcon22nm == "Edgbaston" ~ "South",
                              pcon22nm == "Northfield" ~ "South",
                              pcon22nm == "Hall Green" ~ "Central",
                              pcon22nm == "Selly Oak" ~ "Central")) |> 
  group_by(locality) |> 
  summarise(do_union = TRUE)

# wards
bham_ward25_boundaries <- read_sf(paste0(shape_file_path, "boundaries-wards-2025-wmca.geojson")) |> 
  filter(lad25nm == "Birmingham")

# LSOAs
bham_lsoa21_boundaries <- read_sf(paste0(shape_file_path, "boundaries-lsoa21-bsol.geojson")) |>
  filter(local_authority_name == "Birmingham")


# IMD 2025 by LSOA
bham_imd25 <- read_csv(paste0(data_file_path, "IMD_2025_England.csv")) |> 
  janitor::clean_names() |> 
  filter(local_authority_district_name_2024 == "Birmingham") |> 
  select(lsoa_code_2021, index_of_multiple_deprivation_imd_decile_where_1_is_most_deprived_10_percent_of_lso_as) |> 
  rename(imd25_decile = index_of_multiple_deprivation_imd_decile_where_1_is_most_deprived_10_percent_of_lso_as)

# join LSOA and IMD25 data
bham_imd25 <- bham_lsoa21_boundaries |> 
  left_join(bham_imd25,
            by = join_by("lsoa21cd" == "lsoa_code_2021"))

ward_district_locality_lookup <- read_excel("../data/ward_district_locality_lookup.xlsx") |> 
  janitor::clean_names() |> 
  mutate(district = str_replace(district, " Birmingham", ""),
         locality = str_replace(locality, " Birmingham", ""))

# import postcode lookup to get geopoints for family hubs/PCNs
postcode_lookup <- read_sf(paste0(data_file_path, "postcodes_wmca_dec25.geojson")) |> 
  janitor::clean_names() |> 
  select(postcode, local_authority_name, geometry)

# get family hubs
family_hubs <- read_excel("../data/family_hub_list.xlsx",
                          sheet = "Sheet2") |> 
  janitor::clean_names() |> 
  select(postcode, district_name, hub_name, hub_status, provider)

# add localities to hubs
family_hubs <- ward_district_locality_lookup |> 
  select(locality, district) |> 
  rename(district_name = district) |> 
  distinct(district_name,
           .keep_all = T) |> 
  right_join(family_hubs,
             by = "district_name")

# add geopoints to hubs
family_hubs <- postcode_lookup |> 
  right_join(family_hubs,
             by = "postcode")

# import pcn/gp/locality lookup
bham_pcns <- read_excel(paste0(data_file_path, "bsol_gp_pcn_lookup.xlsx"),
                        skip = 5) |> 
  janitor::clean_names() |> 
  filter(!is.na(code)) |> 
  rename(locality_name = constituency_locality) |> 
  mutate(post_code = str_replace(post_code, "  ", " "))

# add geopoints to PCNs
bham_pcns <- postcode_lookup |> 
  right_join(bham_pcns,
            by = join_by(postcode == post_code))

```

```{r map-setup}
# set up labels

label_districts <- paste0(bham_district22_boundaries$pcon22nm) |> 
  lapply(htmltools::HTML)

label_wards25 <- paste0(bham_ward25_boundaries$wd25nm) |> 
  lapply(htmltools::HTML)
label_wards25_wrap <- gsub("\n", "<br>", paste0(str_wrap(bham_ward25_boundaries$wd25nm, 10))) |> 
  lapply(htmltools::HTML)

label_localities <- paste0(bham_locality_boundaries$locality) |> 
  lapply(htmltools::HTML)

# set colours as variables
highlight_colour <- "red"
border_colour <- "black"
border_sub_colour <- "grey"
ward_text_colour <- "black"
pcon_text_colour <- "black"

# create custom viridis palette
viridis_pal <- viridisLite::viridis(10, begin = 1, end = 0.4)

# set up fill palette for imd25
imd25_pal <- colorNumeric(viridis_pal,
                          domain = bham_imd25$imd25_decile,
                          reverse = F)
```


::: callout-note
## Note

All maps on this page are interactive. You can:

-   zoom in and out using the controls in the top left (or use the scroll wheel on your mouse)
-   hover over the map to see more information
-   use the menu in the top right to move between layers, or turn elements on and off
:::

```{r ward_up_models}

# Build ward-up using best fit to 2022 cons

# first find interactions of wards and 2022 constituencies
district_wards_full <- data.frame()
district_wards <- data.frame()

districts <- bham_district22_boundaries$pcon22nm

for (district in districts) {
  # clip wards inside district boundary
  temp_district_wards <- bham_district22_boundaries |> 
    filter(pcon22nm == district)|> 
    st_intersection(bham_ward25_boundaries) |> 
    mutate(district_name = district)
  
  # find out the area of each clipped ward
  temp_district_wards$area <- st_area(temp_district_wards)
  
  # pull out unclipped wards for this district
  temp_district_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_district_wards$wd25cd) |> 
    mutate(district_name = district)
  
  # find area of unclipped ward and add to clipped ward sf
  temp_district_wards$full_area <- st_area(temp_district_wards_full)
  
  # calulate what % of each ward is inside the boundary
  # then filter out wards with less than 1% area inside boundary
  temp_district_wards <- temp_district_wards |> 
    mutate(pct = area/full_area*100) |> 
    filter(as.numeric(pct) > 1)
  
  # recalculate unclipped wards now wards with <1% are excluded
 temp_district_wards_full <- bham_ward25_boundaries |> 
    filter(wd25cd %in% temp_district_wards$wd25cd) |> 
   mutate(district_name = district)
 
 # append temp dfs to main df
 district_wards_full <- rbind(district_wards_full,
                             temp_district_wards_full)

 district_wards <- rbind(district_wards,
                         temp_district_wards)
}

# use existing df to see which district a ward "belongs" to in terms of greatest percent inside that district
district_wards_best_fit <- district_wards |> 
  as.data.frame() |> 
  select(wd25nm, district_name, pct) |> 
  arrange(desc(pct)) |> 
  distinct(wd25nm,
           .keep_all = T)

# use this to build districts
proposed_bham_districts_best_fit <- bham_ward25_boundaries |> 
  left_join(district_wards_best_fit,
            by = "wd25nm") |> 
  group_by(district_name) |> 
  summarise()

# create ward shape file with assigned districts
district_wards_best_fit_sf <- bham_ward25_boundaries |> 
  left_join(district_wards_best_fit,
            by = "wd25nm")

# district lsoa maps
district_lsoas <- data.frame()

for (district in districts) {
  # clip wards inside district boundary
  temp_district_lsoas <- proposed_bham_districts_best_fit |> 
    filter(district_name == district)|> 
    st_intersection(bham_imd25) |> 
    mutate(district_name = district)

  district_lsoas <- rbind(district_lsoas,
                          temp_district_lsoas)
}

# function to create district map
make_district_ward_map <- function(district) {
  # wrapped ward names for district map
  label_wards25_wrap_district <- district_wards_best_fit |> 
    filter(district_name == district) |> 
    pull(wd25nm) |> 
    str_wrap(15)
  label_wards25_wrap_district<- gsub("\n", "<br>", label_wards25_wrap_district) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside district for district map
  label_wards25_district <- district_wards_best_fit |> 
    filter(district_name == district) |> 
    mutate(label = paste0(wd25nm)) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  district_hubs <- family_hubs |> 
    filter(district_name == district)
  
  label_hubs <- district_hubs |> 
    mutate(label = paste0(hub_name, "<br>",
                          hub_status)) |> 
    pull(label) |>
    lapply(htmltools::HTML)
  
  # lat <- bham_district22_boundaries |> 
  #   filter(pcon22nm == district) |> 
  #   pull(lat)
  # 
  # long <- bham_district22_boundaries |> 
  #   filter(pcon22nm == district) |> 
  #   pull(long)
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("districtPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("wardsTextPane", zIndex = 350) |>
    addMapPane("wardsPane", zIndex = 400) |>     # Wards
    addMapPane("hubsPane", zIndex = 450) |> 
    addTiles(options = tileOptions(opacity = tile_opacity)) |> 
    # display district of interest only
    addPolygons(data = proposed_bham_districts_best_fit |> filter(district_name == district),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.7,
                fillColor = "white",
                options = pathOptions(pane = "districtPane")) |>
    # display IMD by LSOA for district of interest only
    addPolygons(data = district_lsoas |> filter(district_name == district),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.35,
                stroke = T,
                group = "IMD 2025",
                options = pathOptions(pane = "imdPane")) |>
    # full wards text only
    addPolygons(data = district_wards_best_fit_sf |> filter(district_name == district),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_wards25_wrap_district,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "wardsTextPane"),
                group = "Full Wards") |>
    # full wards
    addPolygons(data = district_wards_best_fit_sf |> filter(district_name == district),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                #label = ~wd25nm,
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_wards25_district,
                options = pathOptions(pane = "wardsPane"),
                group = "Full Wards") |>
    addMarkers(data = district_hubs,
               label = label_hubs,
               group = "Family Hubs",
               options = pathOptions(pane = "hubsPane")) |> 
    addLegend(data = district_lsoas,
              "bottomright",
              pal = imd25_pal,
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |>
    # setView(lat = lat, lng = long, zoom = zoom) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025", "Family Hubs"),
      options = layersControlOptions(collapsed = FALSE)) |> 
    hideGroup("IMD 2025")|> 
    hideGroup("Family Hubs")
  
}

# generate localities from districts
proposed_bham_localities_best_fit <- proposed_bham_districts_best_fit |> 
  left_join(ward_district_locality_lookup |> select(district, locality) |> distinct(district, .keep_all = T),
            by = join_by("district_name" == "district")) |> 
  group_by(locality) |> 
  summarise()

# also assign locality to each ward in shapefile
locality_wards_best_fit_sf <- district_wards_best_fit_sf |> 
   left_join(ward_district_locality_lookup |> select(district, locality) |> distinct(district, .keep_all = T),
             by = join_by("district_name" == "district"))

# and get a general lookup of ward -> locality
locality_wards_best_fit <- district_wards_best_fit |> 
   left_join(ward_district_locality_lookup |> select(district, locality) |> distinct(district, .keep_all = T),
             by = join_by("district_name" == "district")) |> 
  as.data.frame()

# locality lsoa maps
locality_lsoas <- data.frame()

localities <- proposed_bham_localities_best_fit$locality

for (loc in localities) {
  # clip wards inside district boundary
  temp_locality_lsoas <- proposed_bham_localities_best_fit |> 
    filter(locality == loc)|> 
    st_intersection(bham_imd25) |> 
    mutate(locality_name = loc)

  locality_lsoas <- rbind(locality_lsoas,
                          temp_locality_lsoas)
}

# function to create locality-ward map
make_locality_ward_map <- function(loc) {
  # wrapped ward names for district map
  label_wards25_wrap_locality <- locality_wards_best_fit |> 
    filter(locality == loc) |> 
    pull(wd25nm) |> 
    str_wrap(15)
  label_wards25_wrap_locality<- gsub("\n", "<br>", label_wards25_wrap_locality) |> 
    lapply(htmltools::HTML)
  
  # labels with % inside locality for locality map
  label_wards25_locality <- locality_wards_best_fit |> 
    filter(locality == loc) |> 
    mutate(label = paste0(wd25nm)) |> 
    pull(label) |> 
    lapply(htmltools::HTML)
  
  # family hub marker setup
  locality_hubs <- family_hubs |> 
    filter(locality == loc)
  
  label_hubs_locality <- locality_hubs |> 
    mutate(label = paste0(hub_name, "<br>",
                          hub_status)) |> 
    pull(label) |>
    lapply(htmltools::HTML)
  
  #PCN setup
  pcn_locality <- bham_pcns |>
    filter(locality_name == loc)
  
  label_pcn_GPs <- paste0(pcn_locality$prac_name, "<br>",
                          pcn_locality$pcn, "<br>",
                          pcn_locality$type)|> 
    lapply(htmltools::HTML)
  
  pal <- colorFactor(
    palette = "Dark2",   # or another palette name
    domain = pcn_locality$pcn
  )
  
  leaflet(width = "100%", height = "650px") |> 
    addMapPane("localityPane", zIndex = 200) |>       # LA boundary layer
    addMapPane("imdPane", zIndex = 300) |>       # IMD layer (bottom)
    addMapPane("wardsTextPane", zIndex = 350) |>
    addMapPane("wardsPane", zIndex = 400) |>     # Wards
    addMapPane("hubsPane", zIndex = 450) |> 
    addMapPane("PCNPane", zIndex = 500) |> 
    addTiles(options = tileOptions(opacity = tile_opacity)) |> 
    # display locality of interest only
    addPolygons(data = proposed_bham_localities_best_fit |> filter(locality == loc),
                color = border_colour,
                weight = 4,
                opacity = 1,
                fillOpacity = 0.7,
                fillColor = "white",
                options = pathOptions(pane = "localityPane")) |>
    # display IMD by LSOA for locality of interest only
    addPolygons(data = locality_lsoas |> filter(locality_name == loc),
                fillColor = ~imd25_pal(imd25_decile),
                fillOpacity = 0.7,
                color = ~imd25_pal(imd25_decile),
                weight = 1,
                opacity = 0.35,
                stroke = T,
                group = "IMD 2025",
                options = pathOptions(pane = "imdPane")) |>
    # full wards text only
    addPolygons(data = locality_wards_best_fit_sf |> filter(locality == loc),
                color = border_colour,
                weight = 0,
                opacity = 0,
                fillOpacity = 0,
                fillColor = "white",
                label = label_wards25_wrap_locality,
                labelOptions = labelOptions(noHide = T, textOnly = T, opacity = 1,
                                            style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                            textsize = "8px",
                                            direction = "center"),
                options = pathOptions(pane = "wardsTextPane"),
                group = "Full Wards") |>
    # full wards
    addPolygons(data = locality_wards_best_fit_sf |> filter(locality == loc),
                color = border_colour,
                weight = 1,
                opacity = 1,
                fillOpacity = 0,
                fillColor = "white",
                #label = ~wd25nm,
                highlightOptions = highlightOptions(
                  weight = 3,
                  color = highlight_colour,
                  bringToFront = TRUE,
                  sendToBack = F),
                label = label_wards25_locality,
                options = pathOptions(pane = "wardsPane"),
                group = "Full Wards") |>
    addMarkers(data = locality_hubs,
               label = label_hubs_locality,
               group = "Family Hubs",
               options = pathOptions(pane = "hubsPane")) |>
    addCircleMarkers(data = pcn_locality,
                     color = ~pal(pcn),
                     fillColor = ~pal(pcn),
                     fillOpacity = 1,
                     radius = 8,
                     stroke = FALSE,
                     label = label_pcn_GPs,
                     group = "PCNs",
               options = pathOptions(pane = "PCNPane")) |> 
    addLegend(data = pcn_locality,
              "bottomleft",
              pal = pal,
              values = ~pcn,
              title = "PCN") |> 
    addLegend(data = locality_lsoas,
              "bottomright",
              pal = imd25_pal,
              values = ~imd25_decile,
              title = "IMD 2025 Decile",
              labFormat = labelFormat(prefix = "Decile "),
              opacity = 0.5) |>
    # setView(lat = lat, lng = long, zoom = zoom) |> 
    addLayersControl(
      overlayGroups = c("IMD 2025", "Family Hubs", "PCNs"),
      options = layersControlOptions(collapsed = FALSE)) |> 
    hideGroup("IMD 2025") |> 
    hideGroup("Family Hubs") |> 
    hideGroup("PCNs")
  
}
```

# All-Birmingham Map

This section shows Birmingham's wards, districts and localities at a whole city level. 

In the map tab, you can see wards, districts and localities. Use the menu in the top right to move between geographies.

The reference table acts as a lookup between all three geographies.

::: panel-tabset

## Map
```{r ward_up_models_district_map}
leaflet(width = "100%", height = "650px") |> 
  addTiles(options = tileOptions(opacity = tile_opacity)) |> 
  addMapPane("LAPane", zIndex = 200) |>       # LA boundary layer
  addMapPane("wardsTextPane", zIndex = 350) |> # Wards
  addMapPane("wardsPane", zIndex = 400) |>   
  addMapPane("districtsTextPane", zIndex = 550) |>
  addMapPane("districtsPane", zIndex = 600) |> # Districts
  addMapPane("localitiesTextPane", zIndex = 650) |>
  addMapPane("localitiesPane", zIndex = 700) |>
  
  # LA boundary
  addPolygons(data = bham_la24_boundaries,
              color = border_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0.7,
              fillColor = "white",
              options = pathOptions(pane = "LAPane")) |>
  
  # Wards
  addPolygons(data = bham_ward25_boundaries,
              color = border_sub_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              label = label_wards25_wrap,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "wardsTextPane"),
              group = "2025 Wards") |>
  
  addPolygons(data = bham_ward25_boundaries,
              color = border_colour,
              weight = 2,
              opacity = 1,
              fillOpacity = 0,
              label = label_wards25,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "wardsPane"),
              group = "2025 Wards") |>
  
  #Districts
  addPolygons(data = bham_ward25_boundaries,
              color = "lightgrey",
              weight = 1,
              opacity = 1,
              fillOpacity = 1,
              fillColor = "white",
              label = label_wards25_wrap,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = "lightgrey"),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "wardsPane"),
              group = "Districts") |>
    # text only
  addPolygons(data = proposed_bham_districts_best_fit,
              color = border_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              fillColor = "white",
              label = ~district_name,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "12px",
                                          direction = "center"),
              options = pathOptions(pane = "districtsTextPane"),
              group = "Districts") |>
  # boundaries
  addPolygons(data = proposed_bham_districts_best_fit,
              color = border_colour,
              weight = 1,
              opacity = 1,
              fillOpacity = 0,
              fillColor = "white",
              label = ~district_name,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "districtsPane"),
              group = "Districts") |> 
  
  # Localities
  addPolygons(data = bham_ward25_boundaries,
              color = "lightgrey",
              weight = 1,
              opacity = 1,
              fillOpacity = 1,
              fillColor = "white",
              label = label_wards25_wrap,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = "lightgrey"),
                                          textsize = "8px",
                                          direction = "center"),
              options = pathOptions(pane = "wardsPane"),
              group = "Localities") |>
    # text only
  addPolygons(data = proposed_bham_localities_best_fit,
              color = border_colour,
              weight = 0,
              opacity = 0,
              fillOpacity = 0,
              fillColor = "white",
              label = ~locality,
              labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, opacity = 1,
                                          style = list("font-family" ="Arial", "font-weight" = "bold", "color" = ward_text_colour),
                                          textsize = "12px",
                                          direction = "center"),
              options = pathOptions(pane = "localitiesTextPane"),
              group = "Localities") |>
  # boundaries
  addPolygons(data = proposed_bham_localities_best_fit,
              color = border_colour,
              weight = 1,
              opacity = 1,
              fillOpacity = 0,
              fillColor = "white",
              label = ~locality,
              highlightOptions = highlightOptions(
                weight = 3,
                color = highlight_colour,
                bringToFront = TRUE),
              options = pathOptions(pane = "localitiesPane"),
              group = "Localities") |>
  addLayersControl(
    baseGroups = c("2025 Wards", "Districts", "Localities"),
    options = layersControlOptions(collapsed = FALSE)
  )
```

## Reference Table
```{r locality-district-ward-table}
locality_wards_best_fit |> 
  as_tibble() |> 
  select(wd25nm, district_name, locality) |> 
  arrange(locality, district_name) |> 
  rename(`Ward name` = wd25nm,
         `District name` = district_name,
         `Locality name` = locality) |> 
  datatable(rownames = F,
            filter = "top",
            options = list(pageLength = 15,
                           autoWidth = TRUE))
```


:::

# Districts

This section shows each district, and its component wards, separately. Each tab shows a different district.

There is the option to view deprivation information (via IMD 2025) and the location of family hubs. Use the menu in the top right to toggle these options on and off.

::: panel-tabset
## Edgbaston

```{r edgbaston-ward-map}
make_district_ward_map("Edgbaston")
```

## Erdington

```{r erdington-ward-map}
make_district_ward_map("Erdington")
```

## Hall Green

```{r hall-green-ward-map}
make_district_ward_map("Hall Green")
```

## Hodge Hill

```{r hodge-hill-ward-map}
make_district_ward_map("Hodge Hill")
```

## Ladywood

```{r ladywood-ward-map}
make_district_ward_map("Ladywood")
```

## Northfield

```{r Northfield-ward-map}
make_district_ward_map("Northfield")
```

## Perry Barr

```{r perry-barr-ward-map}
make_district_ward_map("Perry Barr")
```

## Selly Oak

```{r selly-oak-ward-map}
make_district_ward_map("Selly Oak")
```

## Sutton Coldfield

```{r sutton-ward-map}
make_district_ward_map("Sutton Coldfield")
```

## Yardley

```{r Yardley-ward-map}
make_district_ward_map("Yardley")
```

:::

# Localities

This section shows each locality, and its component wards, separately. Each tab shows a different locality.

There is the option to view deprivation information (via IMD 2025) and the location of family hubs and GP practices/PCNs. Use the menu in the top right to toggle these options on and off.

Note that PCNs are included based on their assigned locality, meaning some practices fall outside of the locality boundary.

::: panel-tabset
## North

```{r north-ward-map}
make_locality_ward_map("North")
```

## East

```{r East-ward-map}
make_locality_ward_map("East")
```

## South

```{r South-ward-map}
make_locality_ward_map("South")
```

## West

```{r West-ward-map}
make_locality_ward_map("West")
```

## Central

```{r Central-ward-map}
make_locality_ward_map("Central")
```

:::



